\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-07 doc/sw-system.tex

\todo{Phil}{Include subject trajectories plot, discuss}

@@

During stage 1 classification of the CFHTLS images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey. We then
assigned two values of the images' posterior probability, $\pr(\LENS|C,T)$, to
define ``detection'' and ``rejection'' thresholds. These were set to be 0.95
and (approximately symmetrically in the logarithm of probability), $10^{-7}$.
Subjects that attained probability of less than the rejection threshold were
scheduled for retirement and subsequently ignored by the analysis code.
Subjects crossing the detection threshold were not retired from the website,
but instead left in the system so that more volunteers could see them.
The analysis code was run every night during the project, and subjects retired
in batches after its completion. This introduced some inefficiency, because
some classifications were accumulated in the time between them crossing the
rejection threshold and the subject actually being retired from the website.
As subjects were retired from the site, more subjects were activated. In this
way, the volunteers who down-voted images for not containing any lensed
features enabled new images to be shown to other members of the community.

>>>>

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
\caption{Typical \SW stage 1 subject trajectories. Subjects drift downwards in
the top panel as they are classified, while being nudged left and right by the
Agents as they interpret the volunteers input. The dotted vertical lines show
(left to right) the retirement threshold, prior probability, and the detection
threshold.}
\label{fig:swap:subject-trajectories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

During stage 1 classification of the CFHTLS images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey. We then
assigned two values of the images' posterior probability, $\pr(\LENS|C,T)$, to
define ``detection'' and ``rejection'' thresholds. These were set to be 0.95
and (approximately symmetrically in the logarithm of probability), $10^{-7}$.
Subjects that attained probability of less than the rejection threshold were
scheduled for retirement and subsequently ignored by the analysis code.
Subjects crossing the detection threshold were not retired from the website,
but instead left in the system so that more volunteers could see them. The
progress of the subjects is illustrated in \Fref{fig:swap:subject-trajectories}.
Subjects appear on this plot at the tip of the arrow, at zero classifications
and prior probability; they then drift downwards as they are classified by the
crowd, with each Agent applying the appropriate kick in probability based on
what it hears its volunteer say. Encouragingly, sims (blue) tend to end up
with high probability, while duds (red) pile up at low probability; test
subjects (black) mostly drift to low probability, but some go the other way.
The latter will help make up the candidate sample. As this plot shows, around
10 classifications are required for a subject to reach the retirement
threshold.

The analysis code was run every night during the project, and subjects retired
in batches after its completion. This introduced some inefficiency, because
some classifications were accumulated in the time between them crossing the
rejection threshold and the subject actually being retired from the website.
As subjects were retired from the site, more subjects were activated. In this
way, the volunteers who down-voted images for not containing any lensed
features enabled new images to be shown to other members of the community.
